Inference of seasonal forcings on reproduction numbers during epidemics

### 2020-04-18 PaperDraft.Rmd
Remove attempt at inline plots
add captions appendix

```{r include=FALSE}
require(cfc19i)

res <- results()
```

@@

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot2.png}
\includegraphics[width=.49\textwidth]{plots/plot3.png}
\includegraphics[width=.49\textwidth]{plots/plot4.png}
\end{center}

$\lambda$ is an adjustment to the model based on the location. What we observe
from the distribution of $\lambda$ is that some locations have much more
certainty in how they deviate from the mean than others. This can be explained
by the unequal distribution of cases across provinces; provinces with more cases
lend themselves to more accurate estimation of $R$.

@@

\begin{center}
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\end{center}

This histogram shows all samples of all entries in the $\varepsilon$ matrix.
Generally, we prefer a lower average spread of $\varepsilon$, because it means
that more of the variation in reproduction number can be predicted from the
seasonal factors, location, and time alone. Unfortunately, we found the observed
spread of $\varepsilon$ is quite high, indicating that there is substantial
variance in reproductive numbers inferred from the data which cannot be
explained by modeled features.

>>>>

@@

\begin{figure}
\includegraphics[width=.49\textwidth]{plots/plot2.png}
\includegraphics[width=.49\textwidth]{plots/plot3.png}
\includegraphics[width=.49\textwidth]{plots/plot4.png}
\caption{Posterior location of $\lambda$, split into three plots for each
location. $\lambda$ is an adjustment to the model based on the location.}
\end{figure}

What we observe from the distribution of $\lambda$ is that some locations have
much more certainty in how they deviate from the mean than others. This can be
explained by the unequal distribution of cases across provinces; provinces with
more cases lend themselves to more accurate estimation of $R$.

@@

\begin{figure}
\includegraphics[width=.49\textwidth]{plots/plot11.png}
\caption{Histogram of all samples of all entires in the $\varepsilon$ matrix.}
\end{figure}

Generally, we prefer a lower average spread of $\varepsilon$, because it means
that more of the variation in reproduction number can be predicted from the
seasonal factors, location, and time alone. Unfortunately, we found the observed
spread of $\varepsilon$ is quite high, indicating that there is substantial
variance in reproductive numbers inferred from the data which cannot be
explained by modeled features.
